\vspace{-2cm} \LARGE Divergence-Free Smoothed Particle Hydrodynamics \\ \large Advanced Simulation and Visualization of Fluids in Computer Graphics

### 2016-12-14 report/paper.tex

\subsection{Divergence solver}
\subsection{Density solver}

>>>>

\subsection{Divergence-Free solver}

\begin{comment}
\begin{lstlisting}[language=C++, mathescape=true, escapeinside={(*}{*)}]
function correctDivergenceError
    for all particles $i$ do
        calculateDensityChange $\frac{Dp}{Dt}_i$
    for all particles $i$ do //Scale $\color{codegreen}a_i$
        $a_i = \frac{a_i}{\Delta t}$
    while (t < $t_{max}$) do //Start simulation loop
        adapt time step $\Delta{t}$ 
        for all particles $i$ do //Predict velocities $\color{codegreen}\mathbf{v}_i^*$
            $\mathbf{v}_i = \mathbf{v}_i + \Delta{t}\mathbf{F}_i^{adv}/m_i$
        correctDensityError($\alpha, \mathbf{v}_i$) //Fulfill $\color{codegreen}\rho^* - \rho_0 = 0$
        for all particles $i$ do //Update positions
            $x_i(t + \Delta{t}) = x_i(t) + \Delta{t}\mathbf{v}_i^*$
        for all particles $i$ do //Update neighbourhoods
            find neighbourhoods $N_i(t + \Delta{t})$
        for all particles $i$ do //Update $\color{codegreen}\rho_i$ and $\color{codegreen}\alpha_i$ 
            compute densities $\rho_i(0)$
            compute factors $\alpha_i(0)$
        correctDivergenceError($\alpha, \mathbf{v}^*$) //Fulfill $\color{codegreen}\frac{D\rho}{Dt} = 0$
\end{lstlisting}
\end{comment}

The divergence-free solver ensures the fluid to be free of density change over time by enforcing $\frac{Dp}{Dt} = 0$, which is equivalent to navier-stokes divergence free condition given in equation %\ref{eq:navier}

\subsection{Density solver}
